An Overview on Temporal Databases.\\ New Approaches and Proposals.

### 2012-02-27 trunk/book/sources/timeDomain.tex
Almost done!

\textcolor{red}{MOVE TO TEMPORAL DATABASE PART}
On the other hand, time may be~\cite{Jensen94thetsql2} \textbf{relative} or \textbf{absolute} (in other words, \textbf{anchored} or \textbf{unanchored}). Sometimes, what one considers \emph{absolute time} is not as definite as one would hope since our concept of absolute time is based on another time reference (for example, January 1st of year one). Relative time has a direction, differently from distance. It is also possible to use negative references so as to represent relative time (e.g. -3 days = three days ago).
\textcolor{red}{END MOVE}

@@

\def\JPicScale{0.5}
\begin{figure}[h]
\centering
\input{graphs/allen.tex}
\caption{Allen relations between two time intervals.}
\label{fig:allen}
\end{figure}

>>>>

%\textcolor{red}{MOVE TO TEMPORAL DATABASE PART}
%On the other hand, time may be~\cite{Jensen94thetsql2} \textbf{relative} or \textbf{absolute} (in other words, \textbf{anchored} or \textbf{unanchored}). Sometimes, what one considers \emph{absolute time} is not as definite as one would hope since our concept of absolute time is based on another time reference (for example, January 1st of year one). Relative time has a direction, differently from distance. It is also possible to use negative references so as to represent relative time (e.g. -3 days = three days ago).
%\textcolor{red}{END MOVE}

@@

\def\JPicScale{0.5}
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{graphs/allen.eps}
\caption{Allen relations between two time intervals.}
\label{fig:allen}
\end{figure}
